Adolescent well-being in the digital age

### 2022-06-30 02-results.Rmd
Don't load anything in .Rprofile
wip 2022-06-30

# Main results

```{r setup}
#| cache: false
# Packages
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(memoise)
library(cachem)
library(posterior)
library(ggh4x)
library(parameters)
library(emmeans)
library(patchwork)
library(multidplyr)
library(tidyverse)

cluster <- new_cluster(3)

cd <- cache_disk("memoise_cache", max_size = Inf)

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)

fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

@@

We then turn to the third research question, to what extent are the changes in well-being, and associations between internet adoption and well-being different between the different demographic groups within adolescents? To answer, Models 1 and 2 also included age and sex as moderators of the trends and associations. In this section, we present results based on the moderated effects.

@@

This figure shows the time courses of each of the six outcome variables. Panels by outcome (rows) and region (columns; including World). Each panel shows the time course by all ages and sex, and on average across ages. So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.

Calculate contrast by sex at the world level.

```{r}
#' Get contrast at average level (no random effects)
#'
#' @param outcome Life_satisfaction etc.
#' @param h Strings representing hypotheses (brm::hypothesis())
#' @param model 1, 2, 3, or 4
get_hyp_avg <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h)$hypothesis
}
get_hyp_avg <- memoise(get_hyp_avg, cache = cd)

h_timecourses <- c(
  Slope_Male = "val_year + val_year:sex1 * -1 = 0",
  Slope_Female = "val_year + val_year:sex1 * 1 = 0"
)

cluster_library(cluster, c("brms", "purrr", "stringr"))
cluster_copy(cluster, c("get_hyp_avg", "h_timecourses"))

timecourses_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()
```

And then for each sex*age at the world level.

```{r}
#' Get contrast for each age
#'
#' @param outcome Life_satisfaction etc
#' @param h brms hypothesis
#' @param model 1,2,3, or 4
get_hyp_age <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
}
get_hyp_age <- memoise(get_hyp_age, cache = cd)
cluster_copy(cluster, "get_hyp_age")

timecourses_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()
```

Combine these to one and plot

```{r}
bind_rows(
  timecourses_world_age %>% 
    unnest(out),
  timecourses_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  mutate(Group = fct_relevel(Group, "Average", "10 to 14")) %>% 
  select(outcome:CI.Upper) %>% 
  separate(Hypothesis, c("Parameter", "Sex")) %>% 
  mutate(s = sign(CI.Lower) == sign(CI.Upper)) %>% 
  ggplot(aes(Group, Estimate, ymin = CI.Lower, ymax = CI.Upper, fill = Sex, col = Sex, group = Sex)) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_y_continuous(
    breaks = extended_breaks(),
    # Effect of 10%
    labels = ~percent(./1000), 
    expand = expansion(.4)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(Group != "Average"),
    aes(), 
    alpha = .2, col = NA
  ) +
  geom_line(
    data = . %>% filter(Group != "Average"),
    aes(group = Sex),
    size = .6
  ) +
  geom_pointrange(
    data = . %>% filter(Group == "Average"),
    position = position_dodge(.75),
    size = .4, fatten = 2.5
  ) +
  facet_wrap(
    "outcome", scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.text.x = element_text(angle = 90),
    legend.position = "none",
    axis.title.x = element_blank()
  )
```

And for all regions too.

First we calculate the contrast by sex for each region.

```{r}
get_region_timecourse_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note 1 for 10 year change
    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_timecourse_avg <- memoise(
  get_region_timecourse_avg, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_avg")
cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
timecourses_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_avg)) %>% 
  collect()
```

Then we calculate the contrasts for each sex*age for each region.

```{r}
get_region_timecourse_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note 1 for decade change
    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | age) + 
        (year*sex | region) + (year*sex | age:region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_timecourse_age <- memoise(
  get_region_timecourse_age, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_age")
timecourses_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_age)) %>% 
  collect()
```

Combine these with world level estimates and plot

```{r}
timecourses_world <- bind_rows(
  timecourses_world_age %>% 
    unnest(out),
  timecourses_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  separate(Hypothesis, c("Parameter", "sex")) %>% 
  select(
    outcome,
    age = Group,
    sex,
    delta = Estimate,
    .lower = CI.Lower,
    .upper = CI.Upper,
  ) %>% 
  mutate(region = "World")

x <- sort(unique(timecourses_world$age))
x2 <- as.character(x)
x2[str_detect(x2, "5 ")] <- ""

bind_rows(
  timecourses_region_age %>% 
    unnest(out),
  timecourses_region_average %>% 
    unnest(out) %>% 
    mutate(age = "Average")
) %>% 
  ungroup() %>% 
  bind_rows(timecourses_world) %>% 
  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
  arrange(sex) %>% 
  select(outcome:.upper) %>% 
  mutate(s = sign(.lower) == sign(.upper)) %>% 
  ggplot(
    aes(
      age, delta, 
      ymin = .lower, ymax = .upper, 
      fill = sex, col = sex, group = sex
    )
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_x_discrete(
    breaks = x,
    labels = x2,
    expand = expansion(c(0.02, 0.05))
  ) +
  scale_y_continuous(
    "Estimated linear change per decade",
    breaks = extended_breaks(),
    labels = ~percent(./100),
    expand = expansion(.1)
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(age != "Average"),
    aes(), 
    alpha = .15, col = NA
  ) +
  geom_line(
    data = . %>% filter(age != "Average"),
    aes(group = sex),
    size = .4
  ) +
  geom_pointrange(
    data = . %>% filter(age == "Average"),
    position = position_dodge(.9),
    size = .3, fatten = 0.1
  ) +
  facet_grid(
    outcome~region, scales = "free_y", 
    labeller = as_labeller(~str_replace(., "_", "\n"))) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "none",
    axis.title.x = element_blank()
  )
agg_png(
  "figures/Fig-timecourses-demographics.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

@@

Calculate contrast by sex at the world level.

```{r}
h_internet_associations <- c(
  Slope_Male = "i1_cw + i1_cw:sex1 * -1 = 0",
  Slope_Female = "i1_cw + i1_cw:sex1 * 1 = 0"
)
cluster_copy(cluster, "h_internet_associations")

internet_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
```

And then for each sex*age at the world level.

```{r}
internet_associations_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
```

And for all regions too.

First we calculate the contrast by sex for each region.

```{r}
get_internet_region_association_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note .1 for 10% change
    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (i1_cw*sex | region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_internet_region_association_avg <- memoise(
  get_internet_region_association_avg, cache = cd
)

cluster_copy(cluster, "get_internet_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
internet_associations_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_avg)) %>% 
  collect()
```

#### Demographics

Then we calculate the contrasts for each sex*age for each region.

```{r}
 get_internet_region_association_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-2.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note .1 for 10% change
    crossing(i1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (i1_cw*sex | age) + 
        (i1_cw*sex | region) + (i1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = i1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_internet_region_association_age <- memoise(
  get_internet_region_association_age, cache = cd
)

cluster_copy(cluster, "get_internet_region_association_age")
internet_associations_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_age)) %>% 
  collect()
```

Combine these with world level estimates and plot

```{r}
internet_associations_world <- bind_rows(
  internet_associations_world_age %>% 
    unnest(out),
  internet_associations_world_average %>% 
    unnest(out) %>% 
    mutate(Group = "Average")
) %>% 
  ungroup() %>% 
  separate(Hypothesis, c("Parameter", "sex")) %>% 
  mutate(
    # Convert to effect of 10% change in internet/mobile
    delta = Estimate/10,
    .lower = CI.Lower/10,
    .upper = CI.Upper/10
  ) %>% 
  select(
    outcome,
    age = Group,
    sex,
    delta,
    .lower,
    .upper,
  ) %>% 
  mutate(region = "World")

internet_associations <- bind_rows(
  internet_associations_region_age %>% 
    unnest(out),
  internet_associations_region_average %>% 
    unnest(out) %>% 
    mutate(age = "Average")
) %>% 
  ungroup() %>% 
  bind_rows(internet_associations_world) %>% 
  mutate(age = fct_relevel(age, "Average", "10 to 14")) %>% 
  mutate(sex = factor(sex, levels = c("Female", "Male"))) %>% 
  arrange(sex) %>% 
  select(outcome:.upper) %>% 
  mutate(s = sign(.lower) == sign(.upper))
internet_associations %>%   
  ggplot(aes(
    age, delta, 
    ymin = .lower, ymax = .upper, 
    fill = sex, col = sex, group = sex)
  ) +
  scale_color_bright() +
  scale_fill_bright() +
  scale_shape_manual(values = c(21, 19), guide = NULL) +
  scale_x_discrete(
    breaks = x,
    labels = x2,
    expand = expansion(c(0.02, 0.06))
  ) +
  scale_y_continuous(
    "Conditional effect of 10% increase\nin per capita internet users",
    breaks = extended_breaks(),
    labels = ~percent(./100),
    expand = expansion(c(.25, .25))
  ) +
  geom_hline(yintercept = 0, lty = 2, size = .2) +
  geom_ribbon(
    data = . %>% filter(age != "Average"),
    aes(), 
    alpha = .15, col = NA
  ) +
  geom_line(
    data = . %>% filter(age != "Average"),
    aes(group = sex),
    size = .4
  ) +
  geom_pointrange(
    data = . %>% filter(age == "Average"),
    position = position_dodge(.9),
    size = .2, fatten = 1.25
  ) +
  facet_grid(
    outcome~region, scales = "free_y", drop = FALSE,
    labeller = as_labeller(~str_replace(., "_", "\n"))) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5),
    legend.position = "none",
    axis.title.x = element_blank()
  )
agg_png(
  "figures/Fig-associations-internet-demographics.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

#### Compare ages

We then compared, for selfharm, the youngest age group's association to all other age group's associations.

```{r}
fit_selfharm <- readRDS("models/brm-Selfharm-3.rds")
h <- hypothesis(fit_selfharm, "m1_cw = 0", scope = "coef", group = "age")
s <- tibble(h$samples)
hypothesis(s, paste0("H1 > H", 2:9))$hypothesis %>% 
  as.data.frame() %>% 
  kbl(digits = 4) %>% 
  kable_custom()
```

#### Forest plot

```{r}
library(ggstance)
internet_associations %>% 
  filter(age == "Average") %>% 
  ggplot(aes(delta, region, col = sex)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.3)
  ) +
  facet_wrap("outcome", scales = "free_x", ncol = 3)
```

@@

This figure shows mobile --> outcome associations. Panels by outcome (rows) and region (columns; including World). Each panel shows the association by all ages and sex, and on average across ages. So we need to calculate four kinds of contrasts: sex\*age | world, sex | world, sex\*age | region, sex | region.

Calculate contrast by sex at the world level.

```{r}
get_hyp_avg <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h)$hypothesis
}
get_hyp_avg <- memoise(get_hyp_avg, cache = cd)

h_mobile_associations <- c(
  # Intercept_Male = "Intercept + sex1 * -1 = 0",
  # Intercept_Female = "Intercept + sex1 * 1 = 0",
  Slope_Male = "m1_cw + m1_cw:sex1 * -1 = 0",
  Slope_Female = "m1_cw + m1_cw:sex1 * 1 = 0"
)

cluster_library(cluster, c("brms", "purrr", "stringr"))
cluster_copy(cluster, c("get_hyp_avg", "h_mobile_associations"))

mobile_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()
```

And then for each sex*age at the world level.

```{r}
get_hyp_age <- function(outcome, h, model) {
  fit <- readRDS(str_glue("models/brm-{outcome}-{model}.rds"))
  hypothesis(fit, h, scope = "coef", group = "age")$hypothesis
}
get_hyp_age <- memoise(get_hyp_age, cache = cd)
cluster_copy(cluster, "get_hyp_age")

mobile_associations_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()
```

Combine these to one and plot

>>>>

# Results

```{r setup, include = FALSE}
#| cache: false
# Packages
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(lme4)
library(broom.mixed)
library(memoise)
library(cachem)
library(flextable)
library(posterior)
library(ggh4x)
library(parameters)
library(emmeans)
library(patchwork)
library(bayestestR)
library(plotly)
library(tidyverse)

# Common options
source("_common.R")
cd <- cache_disk("memoise_cache", max_size = Inf)

oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>%
  mutate(outcome = factor(outcome, levels = oo))

@@

Here, we examine the models to answer

1. To what extent have the well-being and mental health outcomes changed over time
2. To what extent do lagged internet/mobile adoption values predict changes in the outcomes above and beyond the temporal trends
2b. Variance across country, sex, and age in the above
3. Correlations between country-level parameters

```{r}
# Before drawing any plots, we need to extract/compute the relevant parameters from the models. We do that here: For each outcome, we get the countries' average changes over time (in the outcome, internet, and mobile) and associations with internet and mobile
country_post_fun <- function(outcome) {

  fit1 <- readRDS(str_glue("models-small/brm-{outcome}-1.rds"))
  fit2 <- readRDS(str_glue("models-small/brm-{outcome}-2.rds"))
  fit3 <- readRDS(str_glue("models-small/brm-{outcome}-3.rds"))
  fit4 <- readRDS(str_glue("models-small/brm-{outcome}-4.rds"))

  out_outcome_year <- spread_draws(
    fit1,
    b_val_year, r_country__val[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_val_year) %>% 
    mutate(y = "outcome")

  out_internet_year <- spread_draws(
    fit1,
    b_internet_year, r_country__internet[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_internet_year) %>% 
    mutate(y = "Internet")

  out_mobile_year <- spread_draws(
    fit2,
    b_mobile_year, r_country__mobile[country, x] | country
  ) %>% 
    filter(x == "year") %>% 
    ungroup() %>% 
    rename(World = b_mobile_year) %>% 
    mutate(y = "Mobile")

  out_outcome_internet <- spread_draws(
    fit3,
    b_i1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "i1_cw") %>% 
    ungroup() %>% 
    rename(World = b_i1_cw) %>% 
    mutate(y = "outcome")

  out_outcome_mobile <- spread_draws(
    fit4,
    b_m1_cw, r_country[country, x] | country
  ) %>% 
    filter(x == "m1_cw") %>% 
    ungroup() %>% 
    rename(World = b_m1_cw) %>% 
    mutate(y = "outcome")

  out <- bind_rows(
    out_outcome_year, 
    out_internet_year,
    out_mobile_year,
    out_outcome_internet,
    out_outcome_mobile
  ) %>%  
    select(x, y, everything(), -c(.chain, .iteration, .draw)) %>% 
    mutate(across(-c(x, y, World), ~. + World)) %>% 
    rename_with(~str_replace_all(., "\\.(?!\\.)", " ")) %>% 
    mutate(
      x = factor(
        x, 
        levels = c("year", "i1_cw", "m1_cw"),
        labels = c("Time", "Internet", "Mobile")
        )
    )

  out 
}
country_post_fun <- memoise(country_post_fun, cache = cd)
country_post <- fits %>% 
  mutate(
    samples = map(outcome, country_post_fun),
    summary = map(
      samples, 
      ~.x %>% 
        group_by(x, y) %>% 
        summarise_draws(
          mean, 
          ~quantile2(., probs = c(.025, .975)),
          pd = ~pd(as.numeric(.))
        ) %>% 
        rename(country = variable)
    )
  )
```

@@

::: {.panel-tabset .column-body-outset-right}

### Countries

```{r}
#| fig.width: 10
#| fig.height: 8
country_year_plot <- country_coefs %>% 
  filter(x == "Time", y == "outcome") %>% 
  # Arrange each panel
  group_by(outcome) %>% 
  arrange(outcome, mean) %>% 
  mutate(n = 1:n(), y = factor(n)) %>% 
  ungroup() %>% 
  mutate(
    level = country != "World", 
    mh = outcome %in% oo[4:6],
    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
  ) %>% 
  ggplot(aes(mean, y, color = level)) +
  scale_size_manual(values = c(1.25, 0.25)) +
  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
  scale_y_discrete(expand = expansion(.01)) +
  scale_x_continuous(
    "Estimated change per decade",
    breaks = extended_breaks(),
    expand = expansion(.01),
    labels = ~percent(./100)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_segment(
    aes(
      x = q2.5, xend = q97.5, yend = y, 
      text = text
    ),
    size = .15
  ) +
  # Put world in top layer
  geom_point(
    data = . %>% filter(country == "World"), 
    aes(text = text, size = level)
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  labs(y = "Country") +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

country_year_plot
```

### Countries interactive

```{r out.height = 860}
gp <- ggplotly(country_year_plot, tooltip = "text")
gp %>% 
  layout(
    margin = list(t = 40, r = 20, b = 60, l = 30),
    width = 970,
    height = 830
  )
```

### Age and sex

```{r}
#| fig.width: 10
#| fig.height: 8
sex_year_sum <- function(fit) {
  spread_draws(
    fit, 
    b_val_year, `b_val_year:sex1`, r_age__val[age, term] | term
  ) %>% 
    transmute(
      female = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*1,
      male = b_val_year + year + (`b_val_year:sex1` + `year:sex1`)*-1
    ) %>% 
    pivot_longer(-age) %>% 
    group_by(age, name) %>% 
    mean_qi()
}
sex_year_sum <- memoise(sex_year_sum, cache = cd)

sex_year_coefs <- fits %>% 
  mutate(
    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-1.rds"))),
    sex_year = map(fit, sex_year_sum)
  ) %>% 
  select(-fit) %>% 
  unnest(sex_year)

sex_year_plot <- sex_year_coefs %>% 
  mutate(Sex = str_to_title(name)) %>% 
  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
  ggplot(aes(value, age, col = Sex)) +
  scale_color_vibrant() +
  scale_x_continuous(
    "Estimated change per decade",
    breaks = extended_breaks(),
    expand = expansion(.1),
    labels = ~percent(./100)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.35),
    size = .25, fatten = 1.5
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank()
  )
sex_year_plot
```

#### Table

```{r}
country_year_coefs %>% 
  filter(country == "World") %>% 
  mutate(
    across(
      c(mean, q2.5, q97.5), ~percent(./100, .01)
    ),
    pd = percent(pd, .1)
  ) %>% 
  kbl(caption = "Average changes per decade") %>% 
  kable_custom()
```

:::

### Average trends

```{r}
country_year_coefs %>% 
  filter(country == "World") %>% 
  transmute(
    Outcome = str_replace(outcome, "_", " "),
    Trend = str_glue("{number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}]")
  ) %>% 
  kbl(caption = "Estimated world average changes per decade") %>% 
  kable_custom()
```

@@

::: {.panel-tabset}

#### Countries

```{r}
#| fig.width: 10
#| fig.height: 8
country_internet_plot <- country_coefs %>% 
  filter(x == "Internet", y == "outcome") %>% 
  # Arrange each panel
  group_by(outcome) %>% 
  arrange(outcome, mean) %>% 
  mutate(n = 1:n(), y = factor(n)) %>% 
  ungroup() %>% 
  mutate(
    level = country != "World", 
    mh = outcome %in% oo[4:6],
    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
  ) %>% 
  # mutate(star = sign(.lower) == sign(.upper)) %>% 
  ggplot(aes(mean, y, color = level)) +
  scale_size_manual(values = c(1.25, 0.25)) +
  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
  scale_y_discrete(expand = expansion(.01)) +
  # Association with 10% change
  scale_x_continuous(
    "Estimated association with 10% increase in\nper capita internet users",
    breaks = extended_breaks(),
    labels = ~percent(./1000)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_segment(
    aes(
      x = q2.5, xend = q97.5, yend = y, 
      text = text
    ),
    size = .15
  ) +
  geom_point(aes(text = text, size = level)) +
  # Put world in top layer
  geom_point(
    data = . %>% filter(country == "World"), 
    aes(text = text, size = level)
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  labs(y = "Country") +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
country_internet_plot
```

#### Countries interactive

```{r out.height = 860}
gp <- ggplotly(country_internet_plot, tooltip = "text")
gp %>% 
  layout(
    margin = list(t = 40, r = 20, b = 60, l = 30),
    width = 970,
    height = 830
  )
```

#### Age and sex

```{r}
#| fig.width: 10
#| fig.height: 8
sex_internet_sum <- function(fit) {
  spread_draws(
    fit, 
    b_i1_cw, `b_i1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    transmute(
      female = b_i1_cw + i1_cw + (`b_i1_cw:sex1` + `i1_cw:sex1`)*1,
      male = b_i1_cw + year + (`b_i1_cw:sex1` + `i1_cw:sex1`)*-1
    ) %>% 
    pivot_longer(-age) %>% 
    group_by(age, name) %>% 
    mean_qi()
}
sex_internet_sum <- memoise(sex_internet_sum, cache = cd)

sex_internet_coefs <- fits %>% 
  mutate(
    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-3.rds"))),
    sex_internet = map(fit, sex_internet_sum)
  ) %>% 
  select(-fit) %>% 
  unnest(sex_internet)

sex_internet_plot <- sex_internet_coefs %>% 
  mutate(Sex = str_to_title(name)) %>% 
  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
  ggplot(aes(value, age, col = Sex)) +
  scale_color_vibrant() +
  scale_x_continuous(
    "Estimated association with 10% increase in\nper capita internet users",
    breaks = extended_breaks(),
    labels = ~percent(./1000)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.35),
    size = .25, fatten = 1.5
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank()
  )
sex_internet_plot
```

#### Table

```{r}
country_internet_coefs %>% 
  filter(country == "World") %>% 
  mutate(
    across(
      c(mean, q2.5, q97.5), ~percent(./1000, .001)
    )
  ) %>% 
  kbl(caption = "Estimated world associations with 10% increase in internet adoption") %>% 
  kable_custom()
```

:::

@@

::: {.panel-tabset}

#### Countries

```{r}
#| fig.width: 10
#| fig.height: 8
country_mobile_plot <- country_coefs %>% 
  filter(x == "Mobile", y == "outcome") %>% 
  # Arrange each panel
  group_by(outcome) %>% 
  arrange(outcome, mean) %>% 
  mutate(n = 1:n(), y = factor(n)) %>% 
  ungroup() %>% 
  mutate(
    level = country != "World", 
    mh = outcome %in% oo[4:6],
    text = str_glue("{country} ({number(mean, .01)} [{number(q2.5, .01)}, {number(q97.5, .01)}])")
  ) %>% 
  # mutate(star = sign(.lower) == sign(.upper)) %>% 
  ggplot(aes(mean, y, color = level)) +
  scale_size_manual(values = c(1.25, 0.25)) +
  scale_color_manual(values = c("dodgerblue4", "dodgerblue1")) +
  scale_y_discrete(expand = expansion(.01)) +
  # Association with 10% change
  scale_x_continuous(
    "Estimated association with 10% increase in\nper capita mobile broadband subscriptions",
    breaks = extended_breaks(),
    labels = ~percent(./1000)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_segment(
    aes(
      x = q2.5, xend = q97.5, yend = y, 
      text = text
    ),
    size = .15
  ) +
  geom_point(aes(text = text, size = level)) +
  # Put world in top layer
  geom_point(
    data = . %>% filter(country == "World"), 
    aes(text = text, size = level)
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  labs(y = "Country") +
  theme(
    legend.position = "none",
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
country_mobile_plot
```

#### Countries interactive

```{r out.height = 860}
gp <- ggplotly(country_mobile_plot, tooltip = "text")
gp %>% 
  layout(
    margin = list(t = 40, r = 20, b = 60, l = 30),
    width = 970,
    height = 830
  )
```

#### Age and sex

```{r}
#| fig.width: 10
#| fig.height: 8
sex_mobile_sum <- function(fit) {
  spread_draws(
    fit, 
    b_m1_cw, `b_m1_cw:sex1`, r_age[age, term] | term
  ) %>% 
    transmute(
      female = b_m1_cw + m1_cw + (`b_m1_cw:sex1` + `m1_cw:sex1`)*1,
      male = b_m1_cw + year + (`b_m1_cw:sex1` + `m1_cw:sex1`)*-1
    ) %>% 
    pivot_longer(-age) %>% 
    group_by(age, name) %>% 
    mean_qi()
}
sex_mobile_sum <- memoise(sex_mobile_sum, cache = cd)

sex_mobile_coefs <- fits %>% 
  mutate(
    fit = map(outcome, ~readRDS(str_glue("models-small/brm-{.x}-4.rds"))),
    sex_mobile = map(fit, sex_mobile_sum)
  ) %>% 
  select(-fit) %>% 
  unnest(sex_mobile)

sex_mobile_plot <- sex_mobile_coefs %>% 
  mutate(Sex = str_to_title(name)) %>% 
  mutate(age = str_replace_all(age, "\\.(?!\\.)", " ")) %>% 
  ggplot(aes(value, age, col = Sex)) +
  scale_color_vibrant() +
  scale_x_continuous(
    "Estimated association with 10% increase in\nper capita mobile broadband subscriptions",
    breaks = extended_breaks(),
    labels = ~percent(./1000)
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_pointrangeh(
    aes(xmin = .lower, xmax = .upper),
    position = position_dodge2v(.35),
    size = .25, fatten = 1.5
  ) +
  facet_wrap(
    "outcome", 
    nrow = 2, 
    scales = "free_x",
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    axis.title.y = element_blank()
  )
sex_mobile_plot
```

#### Table
